\documentclass[letterpaper,11pt]{article}

\usepackage[letterpaper,left=0.75in,right=0.75in,top=0.7in,bottom=0.7in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\input{glyphtounicode}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}
\pdfgentounicode=1

\begin{document}

{\Large\textbf{Aryan Miriyala}}\\
\href{mailto:aryanmiriyala@gmail.com}{aryanmiriyala@gmail.com} $|$ +1 419-315-0444 $|$
\href{https://www.linkedin.com/in/aryan-miriyala-7788a21b6/}{LinkedIn} $|$
\href{https://github.com/aryanmiriyala}{GitHub}

July 15, 2026

Reddit Ads Engineering Hiring Team

Dear Reddit Ads Engineering Hiring Team,

Reddit's description of itself as a community of communities feels concrete to me. At Bowling Green State University, I founded the Developer Club because I wanted students to have a place where building something of their own was normal. Our weekly meetings grew into a group of more than 15 active students sharing projects, asking for help, and learning from one another. That experience is part of why I am interested in engineering at Reddit: the platform's communities are the product, and the Ads systems behind them have to support that mission without losing sight of the people using them.

My closest technical experience is in backend and data-intensive systems. At AAIS, I built a Python and PySpark billing workflow that processed more than 20 TB of production insurance data for over 700 member companies, and I replaced more than 160 legacy ETL jobs with AWS Glue and S3 pipelines. In an earlier software engineering internship there, I built Python/JSON automation that generated more than 1,000 SQL tables across PostgreSQL, MySQL, and Oracle. I have also built a Dockerized Kafka and Spark streaming pipeline and a C++/OpenMP runtime that collected telemetry, adapted scheduling decisions, and produced performance visualizations. Those projects taught me to validate what a system is doing, communicate tradeoffs clearly, and stay responsible for the unglamorous work that makes it reliable. I would bring that ownership mindset, production data experience, and willingness to learn quickly to Reddit's Ads organization. The opportunity to work on advertiser-facing APIs, campaign measurement, and operational stability is especially compelling because it combines backend engineering with trustworthy data and visible customer outcomes. I would be glad to discuss how my experience can contribute to the team.

Sincerely,\\
Aryan Miriyala

\end{document}
