\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[letterpaper, left=0.2in, right=0.2in, top=0.1in, bottom=0.08in]{geometry}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-3pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.16in, itemsep=0pt, topsep=0pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

\begin{document}

\begin{center}
    \textbf{\LARGE \scshape Aryan Miriyala} \\ \vspace{-2pt}
    \small +1 419-315-0444 $|$
    \href{mailto:aryanmiriyala@gmail.com}{\underline{aryanmiriyala@gmail.com}} $|$
    \href{https://www.linkedin.com/in/aryan-miriyala-7788a21b6/}{\underline{linkedin.com/in/aryan-miriyala}} $|$
    \href{https://github.com/aryanmiriyala}{\underline{\textbf{github.com/aryanmiriyala}}}
\end{center}
\vspace{-18pt}

\section{Professional Summary}
\small{Software engineer and CS graduate student focused on \textbf{data}, \textbf{AI}, and intelligent systems, with experience building \textbf{Python}, \textbf{PySpark}, \textbf{Spark}/\textbf{Hadoop}, \textbf{Docker}, and \textbf{AWS} data workflows. Background includes production cloud ETL, analytics-ready datasets, ML experimentation, RAG/search systems, and reliable internal software.}
\vspace{-5pt}

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Bowling Green State University}{Bowling Green, OH}
    {Master of Science in Computer Science, \textbf{GPA: 4.00/4.00}}{Aug. 2024 -- Aug. 2026}
  \resumeSubheading
    {Bowling Green State University}{Bowling Green, OH}
    {Bachelor of Science in Computer Science, \textbf{GPA: 4.00/4.00}}{Jan. 2021 -- Apr. 2024}
\resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Artificial Intelligence \& Computer Science Intern}{May 2026 -- Present}
      {SmartSolve Industries}{Bowling Green, OH}
      \resumeItemListStart
        \resumeItem{Built secure internal software with \textbf{Next.js}, \textbf{PostgreSQL}, \textbf{Drizzle ORM}, \textbf{SSO}, and auth middleware, organizing onboarding and operations workflows around sensitive employee data.}
        \resumeItem{Created a cross-platform \textbf{Docker} devcontainer for \textbf{WSL2}/\textbf{Colima}, standardizing reproducible local setup for AI-assisted internal software development.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Engineering Intern}{May 2025 -- Aug. 2025}
      {American Association of Insurance Services}{Lisle, IL}
      \resumeItemListStart
        \resumeItem{Automated a manual \textbf{SQL} billing workflow with \textbf{Python}, \textbf{PySpark}, and \textbf{AWS Glue Workflows}, processing \textbf{20+ TB} of golden-table insurance data for \textbf{700+ member companies}.}
        \resumeItem{Built cloud ETL and partitioned \textbf{S3} pipelines that replaced \textbf{160+} legacy Pentaho jobs for \textbf{Semarchy MDM}, improving maintainability and standardizing scalable data movement.}
        \resumeItem{Profiled \textbf{160+} \textbf{MySQL}/\textbf{Oracle}/\textbf{Impala} tables through \textbf{JDBC} with \textbf{Python}, \textbf{Pandas}, and \textbf{SQL}, mapping source-system similarities into \textbf{25} MDM domains.}
        \resumeItem{Implemented reverse-ETL, data-validation, and custom \textbf{AWS IAM} access patterns to support controlled self-service data access and reliable downstream analytics workflows.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Intern}{May 2023 -- May 2024}
      {American Association of Insurance Services}{Lisle, IL}
      \resumeItemListStart
        \resumeItem{Generated \textbf{1,000+} production SQL tables across \textbf{MySQL}, \textbf{Oracle}, and \textbf{PostgreSQL} with \textbf{Python}/JSON workflows, supporting standardized insurance data models across \textbf{10+} lines.}
        \resumeItem{Built \textbf{Python}/\textbf{Pandas} data-processing workflows with multiprocessing, fuzzy matching, and hashing to clean large CSV datasets used in insurance data-standardization pipelines.}
        \resumeItem{Automated database validation with \textbf{AWS Lambda} triggers that tokenized PII using \textbf{hashlib}/\textbf{boto3} and ingested structured JSON into \textbf{S3} for downstream data workflows.}
        \resumeItem{Implemented \textbf{RBAC} and \textbf{JWT} patterns in a \textbf{React}/\textbf{Node.js} modernization effort, replacing broad employee-wide access with role-specific controls for about \textbf{110} users.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Intern}{May 2022 -- Aug. 2022}
      {Alliance for Paired Kidney Donation}{Toledo, OH}
      \resumeItemListStart
        \resumeItem{Improved an \textbf{AWS-hosted} \textbf{Lucee}/\textbf{CFML} healthcare workflow platform with anti-CSRF protection, IP-aware audit logging, protected routing, and data-entry reliability fixes.}
        \resumeItem{Modernized legacy forms with \textbf{HTML5}, JavaScript fallbacks, themed CSS, and reusable modal/tab patterns to improve maintainability for internal clinical operations workflows.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=-1pt, topsep=0pt, parsep=0pt]
  \item\small{\textbf{HealthTrend} $|$ \emph{Apache NiFi, Kafka, Hadoop HDFS, Spark, PySpark, Docker}: Built a Dockerized healthcare data pipeline routing CSV patient records into HDFS and JSON IoT health events into Kafka, then processing both sources with Spark/PySpark for validation and downstream analytics.}
  \item\small{\textbf{MarioRL Agent Comparison} $|$ \emph{Python, PyTorch, Stable-Baselines3, Gym, TensorBoard}: Compared PPO and DQN agents with frame preprocessing, checkpoints, logs, clips, and performance graphs for reward, episode length, and training speed.}
  \item\small{\textbf{FalconGraph Search} $|$ \emph{Python, Flask, OpenAI API, RAG, React, C++}: Built a campus search prototype with document ingestion, chunking, vector retrieval, semantic search, source-aware summaries, and graph-based answer tracing.}
\end{itemize}\vspace{-7pt}

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL, JavaScript/TypeScript, C++/C, C\#, Lucee/CFML} \\
     \textbf{AI/ML}{: PyTorch, TensorFlow, scikit-learn, Stable-Baselines3, TensorBoard, HuggingFace, Sentence Transformers, RAG, embeddings, vector search, semantic retrieval, LangChain, OpenAI API, Mistral AI} \\
     \textbf{Data, Cloud \& Distributed Systems}{: PySpark, Spark, Hadoop HDFS, MapReduce, Kafka, Apache NiFi, AWS Glue, S3, Lambda, IAM, ETL, reverse ETL, data validation, data profiling, partitioned S3 pipelines} \\
     \textbf{Platforms \& Tools}{: Docker, Docker Compose, Git, Linux, PostgreSQL, MySQL, Oracle, Impala, MongoDB, JDBC, React, Node.js}
    }}
 \end{itemize}

\end{document}
