\documentclass[11pt]{letter}
\usepackage[letterpaper, left=0.8in, right=0.8in, top=0.65in, bottom=0.65in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}
\pagestyle{empty}

\begin{document}

\begin{center}
{\Large \textbf{Aryan Miriyala}}\\
\href{mailto:aryanmiriyala@gmail.com}{aryanmiriyala@gmail.com} $|$ +1 419-315-0444 $|$
\href{https://www.linkedin.com/in/aryan-miriyala-7788a21b6/}{linkedin.com/in/aryan-miriyala} $|$
\href{https://github.com/aryanmiriyala}{github.com/aryanmiriyala}
\end{center}

\vspace{0.15in}

Dear Libbey Hiring Team,

Libbey's AI \& Automation Engineer role stands out to me because it is not just about using AI tools in isolation; it is about turning business processes, enterprise content, metadata, security expectations, and stakeholder needs into practical AI workflows that people can trust. The Toledo connection also matters to me. I have studied and worked around Bowling Green and Toledo, including prior software engineering work with Alliance for Paired Kidney Donation, and the chance to contribute to enterprise AI work locally while supporting teams across a global organization is genuinely interesting.

My strongest fit is at the intersection of applied AI, workflow automation, secure internal tooling, and technical enablement. At SmartSolve, I am working on AI-enabled internal software including QMS document relationship planning, a Next.js/PostgreSQL onboarding system with SSO and auth middleware, and Codex/Claude Code-assisted development workflows isolated through Docker. My LLM and RAG projects include FalconGraph Search, which handled web/PDF ingestion, chunking, retrieval, source-grounded answers, and graph relationships, and a diff-grounded PR generation pipeline that used repository evidence and automated evaluation to keep LLM output grounded. I have also built production data automation with Python, PySpark, AWS Glue, Lambda, S3, IAM, and SQL, and supported cybersecurity training and documentation at BGSU. I would bring Libbey a practical builder's mindset: understand the process first, structure the data and metadata correctly, prototype responsibly, document what works, and keep security and governance part of the design from the start.

\end{document}
