\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Aryan Miriyala} \\ \vspace{2pt}
    \small +1 419-315-0444 $|$ 
    \href{mailto:aryanmiriyala@gmail.com}{\underline{aryanmiriyala@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/aryan-miriyala-7788a21b6/}{\underline{LinkedIn Profile}} $|$
    \href{https://github.com/aryanmiriyala}{\underline{GitHub Profile}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Bowling Green State University}{Bowling Green, OH}
    {Master of Science in Computer Science \textbf{GPA: 4.00}}{Aug. 2024 -- May 2026}
  \resumeSubheading
    {Bowling Green State University}{Bowling Green, OH}
    {Bachelor of Science in Computer Science \textbf{GPA: 4.00}}{Jan. 2021 -- Apr. 2024}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Graduate Research Assistant}{Aug. 2024 -- Present}
      {Bowling Green State University}{Bowling Green, OH}
      \resumeItemListStart
        \resumeItem{Led 10 mentors for a spring camp, increasing cybersecurity awareness for 20+ middle school students.}
        \resumeItem{Developed key management and cryptography material for OCRI, benefiting undergraduate students.}
        \resumeItem{Created 10+ labs using Kali Linux and Azure for PKI, key recovery, and penetration testing.}
        \resumeItem{Implemented cipher and secret sharing modules, boosting student problem-solving by 30\%.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Intern}{May 2023 -- May 2024}
      {American Association of Insurance Services}{Lisle, IL}
      \resumeItemListStart
        \resumeItem{Championed JSON structuring, JavaScript transformation, and AWS data optimization, achieving an 80\% efficiency boost for the openIDL project.}
        \resumeItem{Used SQL/PostgreSQL and Python for automated data migration, increasing spreadsheet preparation efficiency by 120\%.}
        \resumeItem{Collaborated with two developers to enhance data accessibility by 50\% through optimized ETL processes.}
        \resumeItem{Modernized AAISDirect using React, JavaScript, Material UI, and Figma, resulting in 40\% faster transactions and 50\% higher client satisfaction.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Intern}{May 2022 -- Aug. 2022}
      {Alliance for Paired Kidney Donation}{Toledo, OH}
      \resumeItemListStart
        \resumeItem{Enhanced kidney-matching software by resolving 20 bugs and integrating Bootstrap, achieving a 30\% performance boost.}
        \resumeItem{Redesigned interface elements with Bootstrap and JavaScript, increasing web app engagement by 40\% and user satisfaction.}
        \resumeItem{Optimized development and deployment using Lucee, PostgreSQL, and Docker on AWS Cloud9, leveraging cloud services effectively.}
        \resumeItem{Bolstered web app security with anti-CSRF tokens, preventing unauthorized access and ensuring data integrity.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{RocketGrades} $|$ \emph{Angular, Node.js, Mistral AI, MongoDB, AWS S3, Auth0, TailwindCSS}}{Mar. 2025}
          \resumeItemListStart
            \resumeItem{Developed a web-based LMS with Mistral AI for instant assignment feedback, cutting grading time and enhancing student learning.}
            \resumeItem{Implemented Auth0 for secure, role-based access control, protecting data privacy for users.}
            \resumeItem{Integrated AWS S3 and MongoDB Atlas for scalable file storage and seamless data retrieval.}
            \resumeItem{Automated assignment grading and feedback using LangChain with Mistral AI, reducing professor workload.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Reinforcement Learning - Super Mario} $|$ \emph{Python, PPO, DDQN, Tensorflow, PyTorch}}{Jan. 2024 - May 2024}
          \resumeItemListStart
            \resumeItem{Developed a reinforcement learning model using PPO and DDQN algorithms, achieving 90\% completion within 200,000 steps.}
            \resumeItem{Optimized environment and reward functions to accelerate training and enhance performance.}
            \resumeItem{Visualized training progress and agent behavior using Jupyter Notebook for performance analysis.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Programming Languages}{: C++, C, C\#, JavaScript, PHP, Java, Python, TypeScript, SQL, PostgreSQL, Oracle} \\
    \textbf{Frameworks \& Libraries}{: React, Angular, React Native, Ionic, Material UI, Daisy UI, Tailwind, Node.js, Flutter, pandas, NumPy, Matplotlib} \\
    \textbf{Developer Tools \& Platforms}{: Git, Docker, VS Code, Visual Studio, , IntelliJ} \\
    \textbf{Databases \& Big Data}{: MongoDB, MySQL, PostgreSQL, Oracle, MapReduce, HDFS, Spark, Pig, Hive}
  }}
\end{itemize}

%-------------------------------------------
\end{document}