\documentclass[letterpaper,11pt]{article}

\usepackage[letterpaper,left=0.80in,right=0.80in,top=0.70in,bottom=0.70in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\input{glyphtounicode}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}
\pdfgentounicode=1

\begin{document}

{\Large\textbf{Aryan Miriyala}}\\
\href{mailto:aryanmiriyala@gmail.com}{aryanmiriyala@gmail.com} $|$ +1 419-315-0444 $|$
\href{https://www.linkedin.com/in/aryan-miriyala-7788a21b6/}{LinkedIn} $|$
\href{https://github.com/aryanmiriyala}{GitHub}

July 17, 2026

Rockwell Automation Hiring Team

Dear Rockwell Automation Hiring Team,

I am applying for the AI Engineer / Architect-IFS Cloud role because it sits where AI, operational workflows, and secure enterprise systems have to work together in a way people can trust. The combination of AI-driven process improvement, maintainable integrations, and disciplined architecture is what draws me to this kind of work.

At SmartSolve, I have been building and planning internal workflow systems where security, maintainability, and operational clarity matter. I architected a Next.js and TypeScript onboarding tracker with PostgreSQL, Drizzle ORM, SSO, and auth middleware to centralize sensitive employee workflows, and I scoped an AI-enabled QMS dependency register by modeling relationships among quality documents so ambiguous operational requirements could become a reviewable system plan. That work taught me to translate business-process needs into concrete application and data decisions instead of treating architecture as an abstract exercise.

At the American Association of Insurance Services, I worked on the data and integration side of long-lived business systems. I automated a manual billing workflow with Python, PySpark, SQL, and AWS Glue across 20+ TB of production insurance data for 700+ member companies, profiled 160+ MySQL, Oracle, and Impala tables into a 25-domain taxonomy, and built validation and access workflows with AWS IAM, Lambda, and S3 to support secure downstream data movement. That experience made me think carefully about data accuracy, lineage, access control, and maintainability across systems that support real business operations.

I have not yet led an IFS Cloud implementation or worked directly with Azure AD and OAuth. What I would bring to Rockwell Automation is adjacent experience designing secure internal systems, role-based workflows, AI-enabled application flows, and enterprise data pipelines, along with a willingness to learn platform-specific details while contributing disciplined architecture and integration thinking.

Sincerely,\\
Aryan Miriyala

\end{document}
