\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[letterpaper, left=0.22in, right=0.22in, top=0.1in, bottom=0.08in]{geometry}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-3pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.16in, itemsep=0pt, topsep=1pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

\begin{document}

\begin{center}
    \textbf{\LARGE \scshape Aryan Miriyala} \\ \vspace{-2pt}
    \small +1 419-315-0444 $|$
    \href{mailto:aryanmiriyala@gmail.com}{\underline{aryanmiriyala@gmail.com}} $|$
    \href{https://www.linkedin.com/in/aryan-miriyala-7788a21b6/}{\underline{linkedin.com/in/aryan-miriyala}} $|$
    \href{https://github.com/aryanmiriyala}{\underline{\textbf{github.com/aryanmiriyala}}}
\end{center}
\vspace{-18pt}

\section{Professional Summary}
\small{Software engineer with experience building reliable backend/data workflows, secure internal tools, and AI-assisted engineering systems using \textbf{Python}, \textbf{SQL}, \textbf{MySQL}, \textbf{PostgreSQL}, \textbf{Oracle}, \textbf{AWS}, and \textbf{Docker}. Background includes production data automation, database validation, access control, reproducible developer environments, and technical tradeoff communication across operational systems.}
\vspace{-5pt}

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Bowling Green State University}{Bowling Green, OH}
    {Master of Science in Computer Science, \textbf{GPA: 4.00/4.00}}{Aug. 2024 -- Aug. 2026}
  \resumeSubheading
    {Bowling Green State University}{Bowling Green, OH}
    {Bachelor of Science in Computer Science, \textbf{GPA: 4.00/4.00}}{Jan. 2021 -- Apr. 2024}
\resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Artificial Intelligence \& Computer Science Intern}{May 2026 -- Present}
      {SmartSolve Industries}{Bowling Green, OH}
      \resumeItemListStart
        \resumeItem{Built secure internal software with \textbf{Next.js}, \textbf{TypeScript}, \textbf{PostgreSQL}, \textbf{Drizzle ORM}, \textbf{SSO}, and auth middleware for onboarding and org-chart workflows around sensitive employee data.}
        \resumeItem{Created a cross-platform \textbf{Docker} devcontainer for \textbf{WSL2}/\textbf{Colima}, standardizing reproducible environments for AI-assisted development, debugging, implementation planning, and code review.}
        \resumeItem{Applied \textbf{Codex} and \textbf{Claude Code} to accelerate system design and feature iteration while validating generated output through human review and proprietary-code isolation.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Engineering Intern}{May 2025 -- Aug. 2025}
      {American Association of Insurance Services}{Lisle, IL}
      \resumeItemListStart
        \resumeItem{Automated a manual \textbf{MySQL}/\textbf{SQL} billing workflow with \textbf{Python}, \textbf{PySpark}, and \textbf{AWS Glue}, processing \textbf{20+ TB} of production insurance data for \textbf{700+} member companies.}
        \resumeItem{Profiled \textbf{160+} \textbf{MySQL}/Oracle/Impala tables with \textbf{Python}, \textbf{Pandas}, \textbf{SQL}, and JDBC to map source-system similarities and define \textbf{25} MDM domains for cloud ETL migration.}
        \resumeItem{Built ETL validation, reverse-ETL, and custom \textbf{AWS IAM} access patterns across \textbf{MySQL}-backed, \textbf{S3}, and MDM workflows, improving issue diagnosis and controlled data access.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Intern}{May 2023 -- May 2024}
      {American Association of Insurance Services}{Lisle, IL}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Python}/JSON backend automation generating \textbf{1,000+} production \textbf{SQL} tables across \textbf{MySQL}, \textbf{Oracle}, and \textbf{PostgreSQL}, supporting standardized data models across \textbf{10+} insurance lines.}
        \resumeItem{Built \textbf{Python}/\textbf{Pandas} workflows with multiprocessing, fuzzy matching, and hashing to clean large CSV datasets for production data-standardization pipelines.}
        \resumeItem{Contributed to a \textbf{React}/\textbf{Node.js} modernization by implementing \textbf{RBAC} and \textbf{JWT} patterns, replacing broad employee-wide access with role-specific controls for roughly \textbf{110} internal users.}
        \resumeItem{Automated event-driven validation for \textbf{MySQL}/Oracle/PostgreSQL rows with \textbf{AWS Lambda}, tokenizing PII using \textbf{hashlib}/\textbf{boto3} and ingesting structured JSON into \textbf{S3}.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Intern}{May 2022 -- Aug. 2022}
      {Alliance for Paired Kidney Donation}{Toledo, OH}
      \resumeItemListStart
        \resumeItem{Secured an \textbf{AWS-hosted} \textbf{Lucee}/\textbf{CFML} healthcare workflow platform with global \textbf{anti-CSRF} protection, IP-aware audit logging, and access-denied/404 routing across form-heavy internal workflows.}
        \resumeItem{Modernized HTML5 date/time inputs, logistics defaults, Matchgrid import ordering, MFI upload paths, and duplicate-antigen crash handling to improve data-entry reliability for internal operations.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=1pt, topsep=1pt, parsep=0pt]
  \item\small{\textbf{HealthTrend Data Pipeline} $|$ \emph{Kafka, Hadoop HDFS, Spark, PySpark, Docker}: Built a containerized healthcare data pipeline routing CSV patient records and JSON health events into batch and streaming processing paths.}
  \item\small{\textbf{Self-Adaptive Parallelism} $|$ \emph{C++, OpenMP, Python, Docker, Linux}: Built a runtime research system using per-epoch telemetry and a UCB controller to tune scheduling policy, chunk size, and thread count.}
  \item\small{\textbf{RocketGrader} $|$ \emph{Angular, TypeScript, Express, MongoDB, Auth0, AWS S3}: Built a full-stack AI feedback platform with REST APIs, role-based dashboards, file upload/storage, parsing, and LangChain/Mistral AI grading workflows.}
  \item\small{\textbf{Diff-Grounded PR Generation} $|$ \emph{Python, OpenAI API, GitHub API}: Built an LLM pipeline generating evidence-grounded PR descriptions from commits, diffs, linked issues, and metadata with automated evaluation against code-change evidence.}
\end{itemize}\vspace{-7pt}

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL, TypeScript/JavaScript, C++, C\#, C, Lucee/CFML} \\
     \textbf{Backend, Databases \& APIs}{: Node.js, Express, REST APIs, PostgreSQL, MySQL, Oracle, MongoDB, Drizzle ORM, JDBC} \\
     \textbf{Cloud, Data \& Systems}{: AWS Glue, Lambda, S3, IAM, PySpark, Pandas, Kafka, Hadoop HDFS, Docker, Git, Linux} \\
     \textbf{Reliability, Security \& AI}{: SSO, JWT, RBAC, Auth0, anti-CSRF, audit logging, PII tokenization, Codex, Claude Code, OpenAI API, Mistral AI, LangChain}
    }}
 \end{itemize}

\end{document}
