\documentclass[11pt]{letter}
\usepackage[letterpaper,margin=0.9in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}
\pagenumbering{gobble}

\begin{document}

\begin{center}
{\Large \textbf{Aryan Miriyala}}\\
\href{mailto:aryanmiriyala@gmail.com}{aryanmiriyala@gmail.com} $|$ +1 419-315-0444 $|$
\href{https://www.linkedin.com/in/aryan-miriyala-7788a21b6/}{linkedin.com/in/aryan-miriyala} $|$
\href{https://github.com/aryanmiriyala}{github.com/aryanmiriyala}
\end{center}

\vspace{0.25in}

Dear Intellicheck Hiring Team,

Intellicheck's Full Stack Software Engineer role stands out to me because the product sits in a space where engineering quality, security, data accuracy, and user trust all matter at the same time. Identity verification for banking, fintech, title insurance, law enforcement, and digital transactions is not just another CRUD workflow; it requires reliable APIs, careful data handling, secure access patterns, and software that can support high-volume real-world decisions. That connects closely with the kind of work I have been building toward through secure internal tools, insurance data workflows, healthcare-adjacent software, and AI-assisted engineering.

My strongest fit is the combination of full-stack product work and production data engineering. At SmartSolve, I built secure internal software with Next.js, TypeScript, PostgreSQL, SSO, and auth middleware while using Codex and Claude Code for implementation planning, debugging, and review. At AAIS, I automated Python, PySpark, and AWS Glue workflows over 20+ TB of insurance data for 700+ member companies, built Python/JSON backend automation that generated 1,000+ SQL tables, contributed to React and Node.js RBAC/JWT modernization, and built AWS Lambda validation flows that tokenized PII into S3. I have also built REST API projects with TypeScript, Express, MongoDB, Auth0, and AWS S3, and worked on security-sensitive AWS-hosted healthcare workflows with anti-CSRF protection, audit logging, and reliability fixes. I would bring Intellicheck a practical full-stack engineering mindset: build clean APIs, protect sensitive workflows, use AI tools responsibly, and stay grounded in measurable product reliability.

\vspace{0.15in}

Sincerely,\\
Aryan Miriyala

\end{document}
