\documentclass[letterpaper,11pt]{article}

\usepackage[letterpaper,left=0.80in,right=0.80in,top=0.70in,bottom=0.70in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\input{glyphtounicode}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{9pt}
\pdfgentounicode=1

\begin{document}

{\Large\textbf{Aryan Miriyala}}\\
\href{mailto:aryanmiriyala@gmail.com}{aryanmiriyala@gmail.com} $|$ +1 419-315-0444 $|$
\href{https://www.linkedin.com/in/aryan-miriyala-7788a21b6/}{LinkedIn} $|$
\href{https://github.com/aryanmiriyala}{GitHub}

July 20, 2026

Texas McCombs Hiring Team

Dear Texas McCombs Hiring Team,

I am applying for the Software Engineer - Full Stack role because it matches the work I have been doing across internal applications, relational data workflows, and production-support-focused software improvements. The role is especially interesting to me because Texas McCombs needs software that supports faculty, staff, students, and business processes in a complex university environment. That combination of practical engineering, data, service orientation, and higher-education impact fits my strongest experience.

At SmartSolve, I architected a Next.js and TypeScript onboarding tracker with PostgreSQL, Drizzle ORM, SSO, and authentication middleware to centralize sensitive HR workflows in a secured internal business application. I also modeled QMS dependency-register requirements across quality documents, which gave me practice turning ambiguous operational needs into reviewable application and data-design plans. That maps closely to the McCombs need for someone who can understand business requirements, design maintainable applications, and collaborate with both technical and non-technical stakeholders.

My data and integration background comes most strongly from the American Association of Insurance Services. I automated a manual SQL billing workflow with Python, PySpark, SQL, and AWS Glue over 20+ TB of production insurance data for 700+ member companies; profiled 160+ MySQL, Oracle, and Impala tables for relational data modeling; and built validation and reverse-ETL workflows with controlled AWS IAM access. In an earlier AAIS software engineering role, I generated 1,000+ production SQL tables from Python/JSON logic and implemented RBAC and JWT patterns in a React/Node.js modernization for about 110 internal users. Those examples reflect the role's emphasis on SQL, data design, integrations, application security, maintainable code, and production validation.

I also bring experience improving internal systems after they are already in use. At the Alliance for Paired Kidney Donation, I modernized an AWS-hosted Lucee/CFML healthcare workflow platform with HTML5, JavaScript, and CSS updates, added anti-CSRF protection and audit logging, and fixed routing, import-ordering, and crash issues affecting internal workflows. As a BGSU Graduate Research Assistant, I wrote cybersecurity lab guides, presentations, and instructor-facing documentation, which strengthened the kind of technical communication that matters in a university setting.

I would bring Texas McCombs a practical full-stack background across JavaScript, TypeScript, Python, SQL, C\#, REST APIs, Git, relational databases, secure workflows, and data validation, along with a willingness to learn the specific Salesforce or Microsoft platform pieces your team uses. I would value the opportunity to help build and support applications that make McCombs' administrative, academic, and student-facing work more reliable.

Sincerely,\\
Aryan Miriyala

\end{document}
