\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
% OPTIMIZED: Replaced your geometry line with this more aggressive one
\usepackage[letterpaper, left=0.35in, right=0.35in, top=0.25in, bottom=0.25in]{geometry}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-9pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% OPTIMIZED: Reduced font size from \huge to \LARGE and used negative vspace
\begin{center}
    \textbf{\LARGE \scshape Aryan Miriyala} \\ \vspace{-2pt}
    \small +1 419-315-0444 $|$ 
    \href{mailto:aryanmiriyala@gmail.com}{\underline{aryanmiriyala@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/aryan-miriyala-7788a21b6/}{\underline{linkedin.com/in/aryan-miriyala}} $|$
    \href{https://github.com/aryanmiriyala}{\underline{\textbf{github.com/aryanmiriyala}}}
\end{center}
% OPTIMIZED: More aggressive vspace pull-up
\vspace{-18pt} % Pulls the "Education" section up


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  % OPTIMIZED: Combined specialization and GPA onto one line
  \resumeSubheading
    {Bowling Green State University}{Bowling Green, OH}
    {Master of Science in Computer Science, \textbf{GPA: 4.00/4.00}}{Aug. 2024 -- Aug. 2026}
  % OPTIMIZED: Combined honors and GPA onto one line
  \resumeSubheading
    {Bowling Green State University}{Bowling Green, OH}
    {Bachelor of Science in Computer Science, \textbf{GPA: 4.00/4.00}}{Jan. 2021 -- Apr. 2024}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Artificial Intelligence \& Computer Science Intern}{May 2026 -- Present}
      {SmartSolve Industries}{Bowling Green, OH}
      \resumeItemListStart
        \resumeItem{Drive an \textbf{AI-first workflow} with agentic CLIs (\textbf{Claude Code}, \textbf{Codex}) as daily drivers to architect, ship, and self-review production features.}
        \resumeItem{Architected a full-stack \textbf{Next.js} onboarding tracker on a \textbf{Postgres}/\textbf{Drizzle ORM} backend, using \textbf{SSO} and \textbf{auth middleware} to protect sensitive new-hire data, cutting HR's manual tracking time and auto-updating the org chart.}
        \resumeItem{Proactively built a cross-platform \textbf{Docker} devcontainer (\textbf{WSL2}/\textbf{Colima}) isolating \textbf{AI agents} to safeguard \textbf{proprietary data}.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Engineering Intern}{May 2025 -- Aug. 2025}
      {American Association of Insurance Services}{Lisle, IL}
      \resumeItemListStart
        % OPTIMIZED: Bullet 1 (Billing) - Locked.
        \resumeItem{Automated a 100\% manual SQL billing script by developing a \textbf{PySpark} job and weekly \textbf{AWS Glue Workflow}, processing \textbf{20+ TB} of \textbf{Impala} data to calculate charges for \textbf{700+ member companies}.}
        
        % OPTIMIZED: Bullet 2 (Architecture) - Locked.
        \resumeItem{Architected the 160+ table migration by profiling \textbf{Oracle/Impala} (via \textbf{JDBC}) with \textbf{Python (Pandas)} and \textbf{SQL} to map \textbf{data similarities} and define a \textbf{single data taxonomy} of \textbf{25 MDM domains}.}
        
        % OPTIMIZED: Bullet 3 (Implementation) - Locked.
        \resumeItem{Replaced \textbf{160+ Pentaho jobs} with an automated \textbf{AWS Glue Workflow}, using the new \textbf{MDM domains} and an \textbf{AWS Glue pipeline} to ETL data into \textbf{S3} (partitioned) for \textbf{Semarchy MDM}.}
        
        % OPTIMIZED: Bullets 4+5 merged to free vertical space.
        \resumeItem{Orchestrated daily \textbf{AWS Glue Workflows} (incl. a \textbf{reverse-ETL} pipeline) to \textbf{enable a new self-service application}, eliminating manual entry and ensuring \textbf{24-hour data latency} across all MDM domains.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Intern}{May 2023 -- May 2024}
      {American Association of Insurance Services}{Lisle, IL}
      \resumeItemListStart
        % OPTIMZED: Bullet 1 - Re-integrated the "scale" metrics (1000s of tables, 10+ lines)
        \resumeItem{Engineered the \textbf{foundational data model} for \textbf{openIDL} (unified insurance-data view), using \textbf{Python} to parse taxonomies into \textbf{1,000s of SQL tables} on \textbf{Oracle/PostgreSQL} across \textbf{10+ insurance lines}.}

        \resumeItem{Built \textbf{Python}/\textbf{Pandas} data-processing workflows with multiprocessing, fuzzy matching, and hashing to clean large CSV datasets for insurance data-standardization pipelines.}

        % OPTIMIZED: Bullet 3 (React) - Locked.
        \resumeItem{Contributed to a full-stack \textbf{React} modernization, implementing \textbf{RBAC} and \textbf{JWT auth} with \textbf{Node.js} for a secure, role-specific landing page serving 100+ internal users.}
        
        % OPTIMIZED: Bullet 4 (Lambda) - Locked.
        \resumeItem{Automated a 2-person validation process by building a \textbf{scheduled AWS Lambda} function that polled database tables, \textbf{tokenized PII using hashlib/boto3}, and ingested clean \textbf{JSON} into S3.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Intern}{May 2022 -- Aug. 2022}
      {Alliance for Paired Kidney Donation}{Toledo, OH}
      \resumeItemListStart
        % OPTIMIZED: Bullet 1 (Security) - 1-Line
        \resumeItem{Ensured \textbf{HIPAA compliance} via site-wide \textbf{anti-CSRF tokens} securing user sessions and patient data.}
        
        % OPTIMIZED: Bullet 2 (New Feature) - 1-Line
        \resumeItem{Built a \textbf{JS/Bootstrap} module to log blood sample data, ensuring data completeness for the matching algorithm.}
        
        % OPTIMIZED: Bullets 3+4 merged (UI/UX + performance) to free a line.
        \resumeItem{Redesigned the responsive \textbf{“Match Run”} page (\textbf{Bootstrap}) and refactored legacy \textbf{JS} to \textbf{async/defer} loading for faster donor-chain rendering.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Travel Health Advisor} $|$ \emph{React, Node.js (Express), MongoDB, Mistral AI, TailwindCSS}}{Apr. 2025}
          \resumeItemListStart
            \resumeItem{Developed a full-stack health app using \textbf{React}, \textbf{TailwindCSS}, and \textbf{Express.js} to provide personalized travel health advisories (e.g., disease risk, precautions) based on user health data and destination.}
            \resumeItem{Built a \textbf{Mistral AI} chatbot and dynamic travel checklist workflow using user health-profile context, disease-risk data, and country-specific vaccine recommendations.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Diff-Grounded PR Description Generation} $|$ \emph{Python, OpenAI API, GitHub API, LLM Evaluation}}{2026}
          \resumeItemListStart
            \resumeItem{Built an LLM research pipeline that generated evidence-grounded GitHub pull request descriptions from commits, file diffs, linked issues, and repository metadata.}
            \resumeItem{Developed structured PR-context construction, grounding-constrained generation, and automated LLM evaluation workflows that improved correctness, coverage, and clarity over baseline descriptions.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd
%
%-----------PROGRAMMING SKILLS-----------
% OPTIMIZED: Replaced the tall 15-line table with this dense, 6-line list
% This saves a massive amount of vertical space.
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, SQL, JavaScript/TypeScript, C++/C, C\#, PHP} \\
     \textbf{AI-First \& Agentic}{: Claude Code, Codex, LangChain, RAG, Mistral AI, HuggingFace, PyTorch, TensorFlow} \\
     \textbf{Data Engineering}{: AWS (Glue, S3, Lambda), Spark (PySpark), Impala, Hadoop (HDFS, MapReduce), Semarchy xDM} \\
     \textbf{Web \& Frameworks}{: React, Next.js, Angular, Node.js, Pandas, NumPy, TailwindCSS} \\
     \textbf{Databases \& Tools}{: PostgreSQL, Oracle, MongoDB, MySQL, Drizzle ORM, Git, Docker, Vercel}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
