\documentclass[letterpaper,11pt]{article}

\usepackage[letterpaper,left=0.80in,right=0.80in,top=0.70in,bottom=0.70in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\input{glyphtounicode}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}
\pdfgentounicode=1

\begin{document}

{\Large\textbf{Aryan Miriyala}}\\
\href{mailto:aryanmiriyala@gmail.com}{aryanmiriyala@gmail.com} $|$ +1 419-315-0444 $|$
\href{https://www.linkedin.com/in/aryan-miriyala-7788a21b6/}{LinkedIn} $|$
\href{https://github.com/aryanmiriyala}{GitHub}

July 16, 2026

Hone Data, Analytics \& Machine Learning Team

Dear Hone Data, Analytics \& Machine Learning Team,

I am applying for the Fall 2026 Data Engineering Intern role because Hone is connecting reliable data work to a concrete healthcare goal: helping people make better decisions about their health. My prior healthcare software and data-pipeline work showed me that accuracy and accessibility are not abstract qualities. They shape whether operational teams can trust the systems they use.

At AAIS, I built production insurance data workflows where billing and master-data processes depended on several large relational sources. I automated a manual SQL billing process with Python, PySpark, and AWS Glue over more than 20 TB of data for 700+ member companies. I also profiled 160+ MySQL, Oracle, and Impala tables, mapped their relationships into 25 MDM domains, and replaced legacy ETL jobs with partitioned cloud pipelines and validation workflows. That experience taught me to understand source data before transforming it and to make reliability part of the pipeline rather than a final check.

I have also built a Dockerized healthcare pipeline that separated patient records and simulated health events into batch and streaming paths using HDFS, Kafka, and Spark/PySpark. Earlier, at the Alliance for Paired Kidney Donation, I improved data-entry and workflow reliability in an AWS-hosted platform supporting transplant operations. I have not used Microsoft Fabric or dbt yet, but I would bring a strong Python, SQL, PySpark, ETL, and relational-modeling foundation, along with experience learning unfamiliar data systems by tracing how their inputs affect downstream users.

I would value the opportunity to contribute to Hone's data team while learning its Fabric lakehouse and helping make healthcare data accurate, reliable, and accessible across analytics, reporting, and product work.

Sincerely,\\
Aryan Miriyala

\end{document}
