\documentclass[letterpaper,11pt]{article}

\usepackage[letterpaper,left=0.80in,right=0.80in,top=0.70in,bottom=0.70in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\input{glyphtounicode}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}
\pdfgentounicode=1

\begin{document}

{\Large\textbf{Aryan Miriyala}}\\
\href{mailto:aryanmiriyala@gmail.com}{aryanmiriyala@gmail.com} $|$ +1 419-315-0444 $|$
\href{https://www.linkedin.com/in/aryan-miriyala-7788a21b6/}{LinkedIn} $|$
\href{https://github.com/aryanmiriyala}{GitHub}

July 16, 2026

Notion Early Career Engineering Team

Dear Notion Early Career Engineering Team,

I am applying for Notion's Software Engineer, New Grad role because the product problems in this posting match the kind of engineering work I keep choosing: turning fragmented workflows into tools that people can actually use, maintain, and build on. Notion's focus on a collaborative AI workspace also feels close to how I have been working recently. At SmartSolve, I built a Next.js and PostgreSQL onboarding tracker with SSO and authentication middleware, and I used Codex and Claude Code as collaborators for planning, debugging, and review while keeping proprietary code isolated. That combination of product judgment, secure workflow design, and pragmatic AI use is the work I want to keep developing.

My strongest fit for the role is full-stack product ownership across user interface, backend services, and data models. In RocketGrader, I built an Angular and TypeScript education platform with Express APIs, MongoDB models, Auth0, AWS S3 file handling, and AI-assisted feedback workflows. In Fix-It-Flow, I built a Next.js PWA with typed API routes, voice and camera input, Gemini Vision, ElevenLabs audio, and DynamoDB session persistence. Those projects taught me to care about more than whether a feature technically works: the flow has to make sense, the data model has to support the experience, and the system has to be understandable enough for someone else to extend.

I would bring Notion an early-career engineer's learning curve, but also real internship experience, strong ownership habits, and a product-minded way of using tools. I am comfortable starting from unclear context, decomposing the problem, asking for help when needed, and pushing toward a clean working system that has real user value.

Sincerely,\\
Aryan Miriyala

\end{document}
