\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[letterpaper, left=0.20in, right=0.20in, top=0.08in, bottom=0.08in]{geometry}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-3pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.16in, itemsep=0pt, topsep=1pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

\begin{document}

\begin{center}
    \textbf{\LARGE \scshape Aryan Miriyala} \\ \vspace{-2pt}
    \small +1 419-315-0444 $|$
    \href{mailto:aryanmiriyala@gmail.com}{\underline{aryanmiriyala@gmail.com}} $|$
    \href{https://www.linkedin.com/in/aryan-miriyala-7788a21b6/}{\underline{linkedin.com/in/aryan-miriyala}} $|$
    \href{https://github.com/aryanmiriyala}{\underline{\textbf{github.com/aryanmiriyala}}}
\end{center}
\vspace{-18pt}

\section{Professional Summary}
\small{Applied AI and software engineer experienced in scoping and shipping \textbf{internal tools}, automations, \textbf{LLM evaluation} workflows, and health- and education-focused systems. Combines \textbf{Claude Code}, full-stack and data engineering, technical training, source-grounded AI judgment, security, and documentation for mixed audiences.}
\vspace{-5pt}

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Bowling Green State University}{Bowling Green, OH}
    {Master of Science in Computer Science, \textbf{GPA: 4.00/4.00}}{Aug. 2024 -- Aug. 2026}
  \resumeSubheading
    {Bowling Green State University}{Bowling Green, OH}
    {Bachelor of Science in Computer Science, \textbf{GPA: 4.00/4.00}}{Jan. 2021 -- Apr. 2024}
\resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Artificial Intelligence \& Computer Science Intern}{May 2026 -- Present}
      {SmartSolve Industries}{Bowling Green, OH}
      \resumeItemListStart
        \resumeItem{Architected a full-stack onboarding tracker with \textbf{Next.js}, \textbf{TypeScript}, \textbf{PostgreSQL}, Drizzle ORM, \textbf{SSO}, and auth middleware to centralize new-hire workflows and protect sensitive employee data.}
        \resumeItem{Developed a sandboxed \textbf{Claude Code} workflow with \textbf{Docker} devcontainers, tmux, and git worktrees to isolate parallel AI agents, compare approaches, and validate generated code before merging.}
        \resumeItem{Scoped an AI-enabled \textbf{QMS dependency register} by modeling relationships among quality documents and using Claude Code/Codex for planning, debugging, and review, clarifying an ambiguous internal need before implementation.}
      \resumeItemListEnd

    \resumeSubheading
      {Graduate Research Assistant I}{Aug. 2024 -- May 2026}
      {Bowling Green State University}{Bowling Green, OH}
      \resumeItemListStart
        \resumeItem{Developed hands-on cybersecurity labs, workshops, and instructor materials using CyberGuardian, the NICE Framework/CAE-CD, Kali Linux, and security tooling, translating complex topics into usable education workflows.}
        \resumeItem{Led \textbf{10 undergraduate students} in delivering a middle-school CyberCamp with phishing demos, password exercises, cryptography labs, and cyber escape-room activities for non-technical learners.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Engineering Intern}{May 2025 -- Aug. 2025}
      {American Association of Insurance Services}{Lisle, IL}
      \resumeItemListStart
        \resumeItem{Automated a manual \textbf{MySQL}/SQL billing workflow with \textbf{Python}, \textbf{PySpark}, and \textbf{AWS Glue}, processing \textbf{20+ TB} of production insurance data for \textbf{700+} member companies.}
        \resumeItem{Profiled \textbf{160+} MySQL/Oracle/Impala tables with Python, Pandas, SQL, and JDBC to map source-system similarities and define \textbf{25} MDM domains for cloud ETL migration.}
        \resumeItem{Built reverse-ETL and validation workflows with \textbf{S3} and custom \textbf{AWS IAM} roles, enabling controlled self-service data access while maintaining 24-hour latency across new MDM domains.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Intern}{May 2023 -- May 2024}
      {American Association of Insurance Services}{Lisle, IL}
      \resumeItemListStart
        \resumeItem{Engineered Python/JSON data-model automation generating \textbf{1,000+} production SQL tables across MySQL, Oracle, PostgreSQL, and \textbf{10+} insurance lines, standardizing repeatable schema creation.}
        \resumeItem{Implemented \textbf{React}/Node.js \textbf{RBAC} and \textbf{JWT} patterns for roughly \textbf{110 users}, replacing broad employee-wide visibility with role-specific access to internal insurance data.}
        \resumeItem{Automated database validation with \textbf{AWS Lambda} triggers that tokenized PII using hashlib/boto3 and ingested structured JSON into \textbf{S3} for downstream standardization workflows.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Intern}{May 2022 -- Aug. 2022}
      {Alliance for Paired Kidney Donation}{Toledo, OH}
      \resumeItemListStart
        \resumeItem{Secured and stabilized an AWS-hosted \textbf{Lucee}/CFML kidney-donation platform through anti-CSRF protection, audit logging, access routing, logistics defaults, and data-import fixes, strengthening clinical workflow security and reliability.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=1pt, topsep=1pt, parsep=0pt]
  \item\small{\textbf{Diff-Grounded PR Description Generation} $|$ \emph{Python, OpenAI API, GitHub API, LLM Evaluation}: Built an ICSME-published pipeline that generated descriptions from repository evidence and outperformed two baselines in correctness, coverage, and clarity.}
  \item\small{\textbf{Travel Health Advisor} $|$ \emph{React, Express, MongoDB, Mistral AI}: Built an end-to-end health AI tool combining disease data, a health-profile-grounded chatbot, risk/vaccine guidance, and downloadable vaccination checklists.}
\end{itemize}\vspace{-7pt}

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{AI \& Evaluation}{: Claude Code, Codex, OpenAI API, Mistral AI, LangChain, RAG, prompt engineering, source-grounded generation, automated LLM evaluation} \\
     \textbf{Software \& Integrations}{: Python, TypeScript/JavaScript, React, Next.js, Node.js, Express, REST APIs, PostgreSQL, MySQL, MongoDB, Oracle} \\
     \textbf{Cloud, Data \& Delivery}{: AWS Glue, Lambda, S3, IAM, PySpark, SQL, Docker, devcontainers, tmux, git worktrees, Git, Linux} \\
     \textbf{Security \& Enablement}{: SSO, JWT, RBAC, anti-CSRF, audit logging, auth middleware, PII tokenization, technical documentation, training demos}
    }}
 \end{itemize}

\end{document}
