\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[letterpaper, left=0.2in, right=0.2in, top=0.1in, bottom=0.08in]{geometry}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-3pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.16in, itemsep=0pt, topsep=0pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

\begin{document}

\begin{center}
    \textbf{\LARGE \scshape Aryan Miriyala} \\ \vspace{-2pt}
    \small +1 419-315-0444 $|$
    \href{mailto:aryanmiriyala@gmail.com}{\underline{aryanmiriyala@gmail.com}} $|$
    \href{https://www.linkedin.com/in/aryan-miriyala-7788a21b6/}{\underline{linkedin.com/in/aryan-miriyala}} $|$
    \href{https://github.com/aryanmiriyala}{\underline{\textbf{github.com/aryanmiriyala}}}
\end{center}
\vspace{-18pt}

\section{Professional Summary}
\small{AI-first software engineer and CS graduate student with experience using \textbf{Codex} and \textbf{Claude Code} for planning, debugging, implementation, and code review while validating generated output. Built \textbf{TypeScript}/\textbf{Python} applications, APIs, databases, AI-enabled workflows, Docker environments, RAG systems, and cloud/data automation with a focus on maintainable, production-minded software.}
\vspace{-5pt}

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Bowling Green State University}{Bowling Green, OH}
    {Master of Science in Computer Science, \textbf{GPA: 4.00/4.00}}{Aug. 2024 -- Aug. 2026}
  \resumeSubheading
    {Bowling Green State University}{Bowling Green, OH}
    {Bachelor of Science in Computer Science, \textbf{GPA: 4.00/4.00}}{Jan. 2021 -- Apr. 2024}
\resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Artificial Intelligence \& Computer Science Intern}{May 2026 -- Present}
      {SmartSolve Industries}{Bowling Green, OH}
      \resumeItemListStart
        \resumeItem{Applied \textbf{Codex} and \textbf{Claude Code} as AI development tools for planning, implementation, debugging, code review, and self-review while keeping human validation central around proprietary code.}
        \resumeItem{Built secure internal software with \textbf{Next.js}, \textbf{TypeScript}, \textbf{PostgreSQL}, \textbf{Drizzle ORM}, \textbf{SSO}, and auth middleware for onboarding, org-chart, and sensitive employee-data workflows.}
        \resumeItem{Created a cross-platform \textbf{Docker} devcontainer for \textbf{WSL2}/\textbf{Colima}, improving reproducible setup, experimentation, and developer workflow consistency for AI-assisted engineering.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Engineering Intern}{May 2025 -- Aug. 2025}
      {American Association of Insurance Services}{Lisle, IL}
      \resumeItemListStart
        \resumeItem{Automated a manual \textbf{MySQL}/\textbf{SQL} billing workflow with \textbf{Python}, \textbf{PySpark}, and \textbf{AWS Glue}, processing \textbf{20+ TB} of production insurance data for \textbf{700+} member companies.}
        \resumeItem{Profiled \textbf{160+} \textbf{MySQL}/Oracle/Impala tables with \textbf{Python}, \textbf{Pandas}, \textbf{SQL}, and JDBC to map source-system similarities and define \textbf{25} MDM domains for cloud ETL migration.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Intern}{May 2023 -- May 2024}
      {American Association of Insurance Services}{Lisle, IL}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Python}/JSON backend automation generating \textbf{1,000+} production \textbf{SQL} tables across \textbf{MySQL}, Oracle, and PostgreSQL, supporting standardized data models across \textbf{10+} insurance lines.}
        \resumeItem{Contributed to a \textbf{React}/\textbf{Node.js} modernization by implementing \textbf{RBAC} and \textbf{JWT} patterns, replacing broad employee-wide access with role-specific controls for roughly \textbf{110} internal users.}
        \resumeItem{Automated event-driven database validation with \textbf{AWS Lambda} triggers that tokenized PII using \textbf{hashlib}/\textbf{boto3} and ingested structured JSON into \textbf{S3}.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Intern}{May 2022 -- Aug. 2022}
      {Alliance for Paired Kidney Donation}{Toledo, OH}
      \resumeItemListStart
        \resumeItem{Secured an \textbf{AWS-hosted} \textbf{Lucee}/\textbf{CFML} healthcare workflow platform with global \textbf{anti-CSRF} protection, IP-aware audit logging, and access-denied/404 routing across internal workflows.}
        \resumeItem{Modernized HTML5 date/time inputs, JavaScript/CSS fallbacks, upload paths, and duplicate-antigen crash handling to improve data-entry reliability for operational users.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
\begin{itemize}[leftmargin=0.15in, label={}, itemsep=0pt, topsep=0pt, parsep=0pt]
  \item\small{\textbf{RocketGrader} $|$ \emph{Angular, TypeScript, Express, MongoDB, Auth0, LangChain, Mistral AI}: Built a full-stack AI feedback platform with REST APIs, role-based dashboards, file upload/parsing, chat, and structured grading workflows.}
  \item\small{\textbf{Diff-Grounded PR Generation} $|$ \emph{Python, OpenAI API, GitHub API}: Built an LLM pipeline generating evidence-grounded PR descriptions from commits, diffs, linked issues, and metadata, with structured context construction and automated evaluation.}
  \item\small{\textbf{FalconGraph Search} $|$ \emph{Python, Flask, OpenAI API, RAG, React, Next.js}: Built a source-grounded search prototype with document ingestion, chunking, vector retrieval, semantic search, LLM answers, and graph-based source tracing.}
  \item\small{\textbf{Travel Health Advisor} $|$ \emph{React, Vite, Express, MongoDB, Mistral AI}: Built a health AI prototype with country-specific disease APIs, saved health-profile context, chatbot answers, and vaccination-checklist PDFs.}
  \item\small{\textbf{DreamScape} $|$ \emph{React Native, Expo, TypeScript, Gemini API, ElevenLabs API}: Built a mobile AI learning app with document summarization, generated quizzes, text-to-speech cues, cached audio, and local-first session tracking.}
\end{itemize}\vspace{-7pt}

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript/JavaScript, Python, SQL, C++, C\#, C, Lucee/CFML} \\
     \textbf{AI-First Development}{: Codex, Claude Code, OpenAI API, Gemini API, Mistral AI, LangChain, RAG, prompt engineering, LLM inference, automated LLM evaluation, embeddings, vector search, semantic retrieval, ChromaDB, Sentence Transformers} \\
     \textbf{Product, APIs \& Databases}{: React, Next.js, Angular, Node.js, Express, Flask, REST APIs, Auth0, JWT, RBAC, SSO, PostgreSQL, MongoDB, MySQL, Drizzle ORM, Mongoose} \\
     \textbf{Cloud, Data \& Tools}{: Docker, Git, Linux, AWS Glue, Lambda, S3, IAM, PySpark, Spark, Pandas, JDBC}
    }}
 \end{itemize}

\end{document}
