\documentclass[letterpaper,11pt]{article}

\usepackage[letterpaper, left=0.8in, right=0.8in, top=0.7in, bottom=0.7in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}
\usepackage{setspace}

\setstretch{1.04}
\pagestyle{empty}

\begin{document}

\begin{center}
    {\Large \textbf{Aryan Miriyala}}\\
    \vspace{2pt}
    +1 419-315-0444 \textbar{} \href{mailto:aryanmiriyala@gmail.com}{aryanmiriyala@gmail.com} \textbar{} \href{https://www.linkedin.com/in/aryan-miriyala-7788a21b6/}{linkedin.com/in/aryan-miriyala} \textbar{} \href{https://github.com/aryanmiriyala}{github.com/aryanmiriyala}
\end{center}

\vspace{10pt}

Dear Hiring Manager,

I am applying for the Graduate Software Engineer role at Fuze Health. I am drawn to Fuze because the company sits at the intersection of digital health, remote care, diagnostics, pharmacy, and the engineering systems needed to make healthcare easier to access and operate. The engineering and data side of that mission is especially interesting to me because my background combines healthcare-adjacent software, cloud data workflows, full-stack feature development, and operational problem solving.

One of my most relevant experiences was at Alliance for Paired Kidney Donation, where I worked on an AWS-hosted Lucee/CFML healthcare workflow platform used for internal transplant operations. I strengthened form security with anti-CSRF protection, added IP-aware audit logging, improved access-denied and 404 routing, modernized legacy date/time inputs, and fixed workflow reliability issues involving import ordering, file locations, duplicate data cases, and clinical logistics defaults. That work gave me practical experience improving sensitive healthcare workflow software where reliability, usability, and clear troubleshooting matter.

I have also worked heavily on cloud and data systems. At AAIS, I automated a manual SQL billing workflow with Python, PySpark, and AWS Glue over 20+ TB of production insurance data, built validation and reverse-ETL workflows, and used AWS Lambda, S3, IAM, Oracle, PostgreSQL, and JSON pipelines to support standardized downstream data flows. Across these roles and projects, I have developed the habit Fuze is looking for: investigate the data, trace the issue, document findings clearly, and turn that understanding into maintainable software improvements.

I would be excited to bring that mix of healthcare workflow experience, AWS/data engineering, full-stack development, and careful communication to Fuze's technology team as it builds products across digital health, diagnostics, and pharmacy. Thank you for your time and consideration.

\vspace{8pt}

Best regards,\\
Aryan Miriyala

\end{document}
